\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity}

### 2013-12-10 docs/paper/paper.tex
Added abstract.

\begin{abstract}
% TODO: Add abstract. Look at slides Peter to see what is asked.
\end{abstract}

@@

\section{Conclusion}

>>>>

\begin{abstract}
In this work we applied PC algorithm on resting-state data of healthy human subjects.
Additionally we propose a variant of PC algorithm that poses weaker assumptions on the model, better fitting the underlying model.
We find that detecting structure homological areas in the brain works better with PC algorithm than most conventional diffusion weighted imaging techniques.
In the area of directionality and causality, more research is needed.
\end{abstract}

@@
